# Analysis
*Lots of regression analysis in this week...*

### Preliminary review of the data

Let's get the data. if you want to know more about the data, please read the manual webpage about it with this [link](http://www.helsinki.fi/~kvehkala/JYTmooc/JYTOPKYS3-meta.txt)
```{r} 
our_data = read.table("/home/iduru/Desktop/IODS-project/learning2014.txt", sep = ",", header = TRUE)
#checking the dimentions of the data
dim(our_data)
#our data has 166 row and 7 columns

#checking the structure of the data
str(our_data)
```
We can see the variable names and values of each samples. 7 total variable and 166 samples are there. 

### Creating the graphical overview of the data
```{r} 
#we will create graphical overview of the data, we need library. so we are calling libraries.

library(ggplot2)
library(GGally)
# graphical overview creting codes.
p <- ggpairs(our_data, mapping = aes(col=gender,alpha = 0.3), lower = list(combo = wrap("facethist", bins = 20)))
p
```
Here we can see correlation of each variables.

### Simple regression analysis. (target is Points)
```{r} 
qplot(attitude, Points, data = our_data) + geom_smooth(method = "lm")
my_model <- lm(Points ~ attitude, data = our_data)
summary(my_model)
```
Here we created a simple regression analysis for the Points and attitude.  
Our formula is Points ~ attitude, we are interested in regression between points and attitude.  
We can see that the slope value calculated as ~3.5 and as we can see in the summary the statistical significance is very high. (t-value)  

### Multiple regression analysis. (target is Points)
```{r}
my_model2 <- lm(Points ~ attitude + stra+ surf, data = our_data)
summary(my_model2)
```
We created a multiple regression with target of Points and variables as attitude, stra, and surf.  
On the summary part we can see that only attitude is statistically significant with the t-value(1.93e-08)  
Other variables are not statistically significant.  
On the next analysis we will remove surf variable which has quite high t value.  

### Multiple regression analysis version 2
```{r}
my_model2 <- lm(Points ~ attitude + stra, data = our_data)
summary(my_model2)
```
Here we made a multiple regression analysis using Points as a target and attitude and stra as variables.  
We can see that intercept slope is statistically significant while stra slope value is not significantly significant.  
R-squared value is some kind of a metric for evaluating the goodness of fit of the model. 1 is the highest score for the R-squared value.  
R-squared value can be useful for estimating of the strength of the relationship between the model and the variable(s). However, it does not show statistical significance.

### Diagnostic plots  
3 different diagnostic plots will be created.  
```{r}
plot(my_model2, which = c(1,2,5), 
     caption = list("Residuals vs Fitted", "Normal Q-Q", "Residuals vs Leverage"))
```
  
1-Residuals vs Fitted, comparing resudual vs model predictions for constant variance of errors. In our case it looks reasonable.  
2-Normal Q-Q plot is testing normality of the errors. In our case normality looks reasonable. We expect that errors are normally distributed.  

